Data: confirmed, dead and recovered. Time series with time step size of one day.
Objective: predict the number of infected people over the next few days.
Infected people = confirmed - (dead + recovered) {the time series for each country/region must be summed for a total}
time_series_19-covid-Confirmed.csv  time_series_19-covid-Deaths.csv  time_series_19-covid-Recovered.csv 
COVID-19/csse_covid_19_data/csse_covid_19_time_series/

Once the data passes the main curve the growth becomes exponetial or linerar?

Train RMSE : 0.07775666232991184
Test RMSE : 0.026243950431177384
Total RMSE : 9104.616950540656


Hyperparameter search for LSTM:
Forecast horizon: 1 - ? (divisible by data size)
Nodes: 5 - 50
Layers: 1 - 5 (NO!)
Loss function: MSE (good for forecasting), all 'mean' functions on Keras.
Optimizer: adam
Dropout:  0 - 1
Epochs: 50 - 1000 (increment by 10) start at 1000 and see where it stops.
Bach size: 1 - ? (divisible by data size)
Activation functions for LSTM layer: tanh (default), ReLU, Swish
Activation functions for Dense layer: tanh (default), ReLU, Swish
EarlyStopping Keras callback.

Notebook structure (table of contents):
Objectives (introduce time series)
|- Predict current infected (total - (dead + recovered)).
|- Predict deceased.
|- How well can the LSTM model the problem? (train on global, test on countries)
|- How does the LSTM perform when compared with other models? (GRU, ARIMA)
Time series analysis
|- Present the data. (tables and graphs, parallel)
|- Why stationary?
|- ADF and KPSS tests.
|- Making the time series stationary.
   |- Differencing.
   |- Gaussian Curve.
Preparing the data for the Neural Network
|- Train and test (data leakage).
|- Supervised learning.
The LSTM
|- Input, hidden and output layers.
|- Training the model. 
|- Does differencing make a difference?
|- Results on global data.
|- Can it generalize? (test on individual countries)
The GRU
|- Input, hidden and output layers.
|- Training the model. 
|- Results on global data.
ARIMA
|- How many integrations?
Summary of results.
|- Plot predictions of all algorithms over the original data.
|- Summarize findings.
